Radial Velocity Upper Limits on Planets around Radio Exoplanet Candidates GJ~1151 and GJ~412A

### 2019-03-01 paper/ms.tex
abstract

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
We don't find a star or giant planet around GJ 1151 or GJ 412A but we cannot rule out anything below 5 $M_\oplus$.

We infer a high resolution spectrum of GJ 1151 which is pretty cool.
\href{https://github.com/benjaminpope/video}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!

@@

We put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ~412A and GJ~1151 respectively at 3.5~\mearth and 5.1~\mearth respectively.

>>>>

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
The recent detection of circularly polarized, variable low-frequency radio emission from the M~dwarfs GJ~412A and GJ~1151 has been interpreted as a Jupiter-like electron cyclotron maser instability arising from star-planet interaction. The existence or parameters of the proposed planets have not been determined. In order to search for these planets, we have obtained new HARPS-N and HPF precise RV data on both stars, and re-analyzed archival Keck-HIRES RV data for GJ~412A.

Using these data we do not detect a clear planetary signal for either star, and we put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ~412A and GJ~1151 at 3.5~\mearth and 5.1~\mearth respectively.

We infer interpolated, high-SNR, high-resolution spectra of GJ~1151.
\href{https://github.com/benjaminpope/video}{\color{linkcolor}\faGithub} % shamelessly borrowed from Luger!

@@
